---
name: Nicholas
surname: Tierney
position: "Lecturer"
address: "Department of Econometrics and Business Statistics"
www: njtierney.com
email: "nicholas.tierney@gmail.com"
twitter: nj_tierney
github: njtierney
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About Me
 
I develop tools with open source software to improve data analysis. My research covers the exploration of missing data methods, longitudinal modelling, location analysis and placing facilities, modelling geospatial cardiac risk.

# Education

```{r education}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Bachelor of Psychological Science (Honours)", "2008-2012", "University of Queensland", "Brisbane, Australia",
  "PhD (Statistics)", "2013-2018", "Queensland University of Technology", "Brisbane, Australia"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Software

```{r software}
tribble(
  ~ pkg, ~ when, ~ role, ~ details,
  "naniar", "2017 - ", "Lead developer", "Tidy data structures, summaries, and visualisations for missing data",
  "visdat", "2017 - ", "Lead developer", "Preliminary exploratory visualisation of data",
  "brolgar", "2019 - ", "Lead developer", "Tools browse over longitudinal data graphically and analytically",
  "mmcc", "2016 - ", "Lead developer", "Fast and tidy methods for summarising mcmc chains using data.table.",
  "maxcovr", "2017 - ", "Lead developer", "Tools for location analysis and solving the Maximal Coverage Location Problem",
  "broomstick", "2017 - ", "Lead developer", "Convert decision tree objects into tidy data frames",
  "ukpolice", "2018 - ", "Author", "Download Data on UK Police and Crime",
  "syn", "2018 - ", "Lead developer", "A zero dependency R package that lists synonyms and antonyms.",
  "ishiara", "2020 - ", "Lead developer", "Generate colourblindness (Ishihara) plates in R",
) %>% 
  brief_entries(glue::glue("\\textbf{<pkg>}: <role> \\newline <details>", .open = "<", .close = ">"), when, .protect = FALSE)
```


# Awards

```{r awards}
tribble(
  ~Year, ~Type, ~Desc,
  2017, "PhD", "Thesis nominated for University Doctoral Outstanding Thesis Award.",
  2013, "PhD", "APA ($24,500 Annually for 4 years)",
  2013, "PhD", "IDTC Top Up ($10,000 Annually for 4 years)",
  2015,  "Teaching", "Winner of Sessional Teaching and Reflection Showcase (STARS) talk 'The Joy of Stats'",
  2015, "Teaching", "Vice-Chancellor's Performance Award__ for innovation in teaching in SEB113 ($2,500)",
  2018, "Presenting", "EJC Pitman Prize (Runner Up), The Stastistical Society of Australia",
  2018, "Grant", "A unified platform for missing values methods and workflows ($10,000 USD)",
  2019, "Grant", "A unified platform for missing values methods and workflows (renewed from 2018 again) ($10,000 USD)",
  2019, "Grant", "ACEMS International Mobility Programme ($10,000 AUD)"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

# Publications

```{r pubs}
library(dplyr)
pubs <- scholar::get_publications("o4eVsQEAAAAJ&hl") %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", 
            author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), 
            year, 
            key = row_number()) %>% 
  filter(key != 15) %>% 
  mutate(journaltitle = case_when(key == 21 ~ "Honours Thesis",
                                  TRUE ~ journaltitle))

pubs %>% 
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("njtierney.bib")

bibliography_entries("njtierney.bib")
```

# Presentations


- [2020/06/26: "The use of colour in graphics: A journey through the body & mind to the screen"](https://njt-monash-colour.netlify.app/#1)
- [2020/02/14: "Data Data Data, Invited Seminar at University of Washington, Seattle, USA"](https://njt-data-uw.netlify.app/#1)
- [2020/02/12: "Data Data Data, Guest Speaker at Sage Bionetwords, Seattle, USA"](https://njt-sage.netlify.app/#1)
- [2020/01/29: "Making Better Spaghetti, Invited Speaker at rstudio::conf2020"](https://njt-rstudio20.netlify.app/#1) [[github]](https://github.com/njtierney/rstudioconf20) [[video]](https://rstudio.com/resources/rstudioconf-2020/making-better-spaghetti-plots-exploring-the-individuals-in-longitudinal-data-with-the-brolgar-pac/)

`2019` Exploring and understanding the individual experience from longitudinal data, or ... How to make better spaghetti (plots) (OzVis 2019, Brisbane (**Keynote speaker**)

`2019` Exploring and understanding the individual experience from longitudinal data, or ... How to make better spaghetti (plots) (**Invited Seminar at ANU, Canberra**)


`2018` [**RUCK: R Users Conference Korea (Invited Keynote speaker)** "Empowering people with community, software, and peer review".](https://talks.updog.co/korea-keynote/korea-keynote.html#1)

`2018` **ISCBASC** "Now you see it?  Now you don’t?  The role of graphics in identifying MCMC convergence", Melbourne, Australia [HTML](https://talks.updog.co/asc2018/talk-mcmclineup-keynote/index.html) [PDF](https://talks.updog.co/asc2018/pdf/talk-mcmclineup-keynote.pdf)

`2018` Genentech, California, USA. February 15. Presented a talk "Why is that missing, and what can we do about it? Tools for missing data and beyond". (**invited speaker**)

`2018` **UseR!**"Find the best locations for facilities using `maxcovr`", Brisbane, Australia [Slides](https://talks.updog.co/user2018-maxcovr/user2018-maxcovr-talk.html#1 ) [YouTube](https://www.youtube.com/watch?v=sA8ItKmdwjM&t=3s)

`2017` [**UseR!**  Narnia: Data structures and functions for consistent exploration of missing data, Brussels, Belgium](https://talks.updog.co/user2017/2017-07-06-user.html#1)

`2017` [**Angletr** "Narnia: Data structures and functions for consistent exploration of missing data" Anglet, France](https://talks.updog.co/2017-angletr/2017-06-02-tidy-miss.html#1)

`2017` [**Wombat / MeDaScin** Tidy Approaches to Missing Data, Melbourne, Australia](https://talks.updog.co/wombat2017/2017-06-02-tidy-miss.html#1)

`2016` Gates-Cambridge Group, Cambridge University, England. July 20 - July 23. Presented a 2-hour workshop "Interactive Maps in R: Getting a lay of the land", on using R for the exploration and visualisation of geospatial data. (**invited speaker**)

`2016` [**Università della Svizzera italiana Lugano** "Data Mining Mining Data: Statistical Approaches in Occupational Health for a Mining Site" __Nicholas Tierney__](https://speakerdeck.com/njtierney/data-mining-in-mining-data-statistical-approaches-in-occupational-health-surveillance-for-a-mining-site).

`2016` [**Workshop Organised by Monash Business Analytics Team (WOMBAT)** "Be a Hawk Not a Turkey: How A Bird's Eye View can Streamline Data Analysis", __Tierney, N.J.__ Melbourne Zoo, Melbourne, Australia.](https://speakerdeck.com/njtierney/be-a-hawk-not-a-turkey-how-a-birds-eye-view-of-your-data-can-streamline-data-analysis)

`2014` [**ASC / IMS Meeting** __Tierney, N.J.__,  Mengersen, K., Pitchforth, J. "Understanding Missing Data: The Use of Classification and Regression Trees, and Boosted Regression Trees", _Sydney, Australia_.](https://speakerdeck.com/njtierney/understanding-missing-data-the-use-of-classification-and-regression-trees-and-boosted-regression-trees)

### Posters

`2019` "A Missing Data Carol: Ghosts of Missing Data Past, Present, and Future". **Tierney, NJ** _rstudioconf2019, Austin, Texas, USA_ [PDF](https://talks.updog.co/2019-01-16-missing-data-past-present-future.pdf)

`2018` "Tidy Principles for Missing Data Exploration using `naniar`" **Tierney, NJ.** _rstudioconf18, San Diego, USA_. [PDF](https://njtierney.updog.co/img/rstudioconf18-tidy-principles-for-missing-data.pdf)

`2017` "Now you see it? Now you don't? The role of graphics in identifying MCMC convergence" **Tierney, NJ.**, Cook, D, McBain, M. _Bayes on the Beach, Gold Coast, Australia_. [PDF](https://njtierney.updog.co/img/2017-11-29-poster-ppt-botb.pdf)

`2016` "Bayesian Approaches in Occupational Health Surveillance" **Tierney, N.J.**, Mengersen, K., Clifford, S., Drovandi, C., Harden, F., Harden, M. _World Meeting for the International Society for Bayesian Analysis_.

`2015` "The Sharpest Tool in the Shed" **Tierney, N.J.**, Mengersen, K., Harden, F., Harden, M. _Bayes on the Beach_.

`2015` ["Integrating Occupational Hygiene, Medicine and Engineering in a Mining Context." Harden, M., Steer, C., Harden, F., Butler, G., Mengersen, K., __Tierney, N.J.__, _Ann. Occup. Hyg., Vol. 59, No. Supplement 1, 1–47 doi:10.1093/annhyg/meu119_](https://annhyg.oxfordjournals.org/content/59/suppl_1/1.full.pdf+html). (Peer Reviewed Poster).

`2014` "Missingness, Mixtures, and Multiple Imputation" **Tierney, N.J.**, Mengersen, K., Harden, F., Harden, M. _Bayes on the Beach_.

## Blog

`2013-` I maintain a personal blog, [njtierney.com](https://www.njtierney.com), to share code and statistics, and to engage in dialogue with the statistics and r-programming communities.



## Professional Experience

## Invited Academic

`2020` Berkeley Institute of Data Science (BIDS), Berkeley, California, USA, Feb 3 - Feb 3. Continued collaboration with Dr Karthik Ram on best practices for publishing data sources, and current technology issues in modern data science.

`2019` Berkeley Institute of Data Science (BIDS), Berkeley, California, USA, Jan 24 - Feb 13. Continued collaboration with Dr Karthik Ram on best practices for publishing data sources, and current technology issues in modern data science.

`2019` Johns Hopkins Bloomberg School of Public Health, Maryland, USA, Jan 2 - Jan 13. Collaboration with Prof. Roger Peng on approaches for understanding and measuring MCMC convergence and diagnostics.

`2018` Berkeley Institute of Data Science (BIDS), Berkeley, California, USA, Feb 5 - Feb 9. Collaboration with Dr Karthik Ram on best practices for publishing data sources, and current technology issues in modern data science.

`2017` Inter-Disciplinary Institute of Data Science at Università della Svizzera italiana (USI), Lugano, Switzerland, July 10 - July 14. Continuing Collaboration with Professor Antonietta Mira of USI and Professor Angelo Auricchio of the Center for Computational Medicine in Cardiology (CCMC) on optimising placement of Automatic Electronic Defibrillators (AEDs) in Switzerland.

`2016` Inter-Disciplinary Institute of Data Science at Università della Svizzera italiana (USI), Lugano, Switzerland, June 18 - July 9. Collaboration with Professor Antonietta Mira of USI and Professor Angelo Auricchio of the Center for Computational Medicine in Cardiology (CCMC) on optimising placement of Automatic Electronic Defibrillators (AEDs) in Switzerland.

### Science Communication

`2016` ["Science Meets Parliament"](https://scienceandtechnologyaustralia.org.au/focus-on/science-meets-parliament-2016/), Canberra, Australia, __fully sponsored travel__ provided by [SSA](https://www.statsoc.org.au/). [Blog post write up of event](https://www.njtierney.com/post/2016/08/22/stats-meets-parliament/)

`2013` ["Statistics for Journalists", _Australian Science Media Centre_ Brisbane, Australia](https://www.njtierney.com/post/2013/11/01/stats-for-journo/).

### Conferences

`2019` Assistant Organiser of the fourth [rOpenSci Unconference in Australia](ozunconf19.ropensci.org).

`2018` Principal Organiser of the third [rOpenSci Unconference in Australia](ozunconf18.ropensci.org).

`2018` Member of the Organising Committee for [UseR!2018](https://user2018.r-project.org/), Brisbane, Australia.

`2017` Principal Organiser of the second [rOpenSci Unconference in Australia](ozunconf17.ropensci.org).

`2016` Principal Organiser of the first [rOpenSci Unconference in Australia](auunconf.ropensci.org).

### Statistics Society of Australia

`2017-2019` [SSA](https://www.statsoc.org.au/) General Committee Member for Victorian Branch of SSA.

`2013-16` [SSA](https://www.statsoc.org.au/) Assistant Chair of Biostatistics.

`2013-16` [SSA](https://www.statsoc.org.au/) Young Statisticians Representative for Queensland.

### Meeting Chair

`2017-2019` Meeting Chair for [Non-Uniform Monash Business Analytics Team (NUMBAT), Monash](https://numbat.space/).

`2014` Meeting Chair for [Bayesian Research and Applications Group (BRAG), QUT](https://bragqut.wordpress.com/).

### Talks (Outside of conferences)

# Technical skills

* R
* STATA
* greta
* LaTeX
* Git + GitHub
* Bayesian Statistics
* Data Visualisation
* Exploratory Data Analysis
* Reproducible Reporting

## Extra-Curricular

### Climbing

`2014-2019` Master of Ceremonies at State and National Climbing Championships.

`2014-` Archivist of the UQMC.

`2015` Magazine Editor of the UQMC.

`2012,14` Executive Committee of the [University of Queensland Mountain Club (UQMC)](https://uqmc.org/).

`2014` Appointed Honourary Life Member of the UQMC.



## Teaching

### ETC1010

`2019-2020` "Introduction to Data, Modelling, and Computing". Lecturer. Revised content, developed new assignments, and written and practical exams.

### SEB113

`2015` "Statistical Methods for Science". Developed computer lab material with RMarkdown, produced instructional videos, and taught workshops.

### Software Carpentry

`2018-2019` Software carpentry instructor trainer. Involved in teaching best 
  practices on how to teach software coding to other instructors.

### DataCamp

`2018` Developed online course on Handling Missing Data. Produced tutorials and
  instructional videos.
  
### R markdown for scientists

`2018 - 2019` A 3-4 hour workshop aimed at getting researchers up to speed with modern approaches to reproducible research with the Rmarkdown software + Rstudio. This course has been run five times in two states of Australia. Course materials are made completely free and open source online at: https://rmd4sci.njtierney.com/

### Invited Tutorials

`2018-19` ["Rmarkdown for scientists"](https://rmd4sci.njtierney.com/), (Delivered five times in Canberra and Melbourne since November 2018 - November 2019)

`2018` [Missing Data Imputations, _UseR!2018_, Brisbane, Australia.](https://user2018.r-project.org/tutorials/)

`2017` Reproducible Reporting Using RMarkdown and GitHub, _Angletr_, Anglet, France.

`2015` Developing Bayesian Models for Ranking Academic Papers, _Bayes on the Beach_, Gold Coast, Australia.
